---
title: "Example_Use"
author: "Thomas Gaertner"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This R Markdown document shows the usage of the package 'cino1'. 

```{r}
library(cinof1)
```


## Data

In this package, a sample data frame is included. It contains data for 300 patients within an n of 1 study. The data has the following structure:

* patient_id
* date`
* day
* Block
* Activity
* treatment
* Uncertain_Low_Back_Pain

```{r data}
load("data/simpatdat.rda")
summary(simpatdat)
```

## Basic Analysis

Basic functions for analyse N-of-1 studys are for example wilcox test or comparative plots. These two functions are provided in this package.

```{r basic functions}
outcome <- "Uncertain_Low_Back_Pain"
exposure <- "treatment"
comparative_plot(simpatdat, exposure = exposure, outcome = outcome)
wilcox.nofone(simpatdat, exposure = exposure, outcome = outcome)
```
## G-Estimation

```{r g-estimation}
outcome <- "Uncertain_Low_Back_Pain"
exposure <- "treatment"
comparative_plot(simpatdat, exposure = exposure, outcome = outcome)
wilcox.nofone(simpatdat, exposure = exposure, outcome = outcome)
```
